Non-kissing complexes and tau-tilting for gentle algebras

### 2018-07-13 firstPaper/firstPaperShort/nonKissingComplex.tex
footnotes in Table 1
corrections

\begin{example}
A gentle bound quiver~$\bar Q\ex$ and its blossoming gentle bound quiver~$\bar Q\ex\blossom$ are represented in \fref{fig:exmBlossomingQuiver}.
\vspace*{-.4cm}

\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=.7]{exmBlossomingQuiver}}
	\caption{A gentle bound quiver~$\bar Q\ex$~(left) and its blossoming gentle bound quiver~$\bar Q\blossom\ex$~(right). Blossom vertices are white and blossom edges are thin.}
	\label{fig:exmBlossomingQuiver}
\end{figure}
\end{example}

@@

\begin{definition}
A \defn{walk} of~$\bar Q$ is a maximal string in~$\bar Q\blossom$ (thus joining two blossom vertices of~$\bar Q\blossom$).
We denote by~$\walks(\bar Q)$ the set of all walks on~$\bar Q$.
Note that~$\walks(\bar Q)$ is finite if and only if~$\bar Q$ has a relation in any non-kissing cycle.
As for strings, we often implicitly identify the two inverse walks~$\omega$ and~$\omega^{-1}$, and we let~$\walks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \walks(\bar Q)}$ denote the set of undirected~walks.
\end{definition}

\begin{example}
\fref{fig:exmFacet} shows many examples of walks on the gentle quiver~$\bar Q\ex$ of \fref{fig:exmBlossomingQuiver}.
\end{example}

@@

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=1.4]{exmBijectionAssociahedron}}
	\caption{An oriented path~$\bar Q\pa$ is simultaneously a triangulation and a grid bound quiver (left). A facet of the reduced non-kissing complex~$\RNKC[\bar Q\pa]$ can be seen equivalently as a triangulation or as a collection of non-kissing south-east paths (right).}
	\label{fig:exmBijectionAssociahedron}
\end{figure}

@@

\begin{example}
\fref{fig:exmFacet}~(left) provides examples of kissing and non-kissing walks.
%
\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.7]{exmFacet}}
	\caption{(Left) Three walks on the quiver~$\bar Q\ex$ of \fref{fig:exmBlossomingQuiver}: the dotted red and orange walks are non-kissing, but both kiss the plain blue walk. (Right) A maximal collection~$F\ex$ of pairwise non-kissing walks on the quiver~$\bar Q\ex$: the thin light blue walks are straight, the others~are~bending.}
	\label{fig:exmFacet}
\end{figure}
\end{example}

@@

\begin{example}
\fref{fig:exmFacet}\,(right) shows a facet~$F\ex$ of the non-kissing complex~$\NKC[\bar Q\ex]$ for the quiver~$\bar Q\ex$ of \fref{fig:exmBlossomingQuiver}.
The reduced non-kissing complexes of all connected gentle bound quivers with~$2$ vertices are illustrated on \fref{fig:all2}.
The reduced non-kissing complexes of two gentle bound quivers with~$3$ vertices are illustrated on \fref{fig:exmNKC}\,(left).
\end{example}

@@

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.7]{exmFlip}}
	\caption{The flip of the orange walk~$\omega$ in the facet~$F\ex$ of \fref{fig:exmFacet}. The other two walks~$\mu, \nu$ of~$F\ex$ involved in the flip are the yellow and green walks. The distinguished arrows on each walk of~$F\ex$ are marked with triple arrows.}
	\label{fig:exmFlip}
\end{figure}

@@

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.45]{exmBiclosed}}
	\caption{Four sets of strings on the gentle bound quiver~$\bar Q\ex$ of \fref{fig:exmBlossomingQuiver}\,(left). The first is neither closed not coclosed, the second is closed but not coclosed, the third is coclosed but not closed, and the fourth is biclosed.}
	\label{fig:exmBiclosed}
\end{figure}
\end{example}

@@

\begin{figure}[t]
	\capstart
	\centerline{
	\begin{overpic}[scale=.45]{exmProjections}
			\put(30,6){$\longleftarrow$}
			\put(31,8){$\projDown$}
			\put(68,6){$\longrightarrow$}
			\put(69,8){$\projUp$}
			\put(12,-3){$\projDown(S\ex)$}
			\put(50,-3){$S\ex$}
			\put(85,-3){$\projUp(S\ex)$}
	\end{overpic}
	}
	\vspace{.3cm}
	\caption{A biclosed set of strings~$S\ex \in \Bicl{\bar Q\ex}$ (middle) and its images~$\projDown(S\ex)$ (left) and~$\projUp(S\ex)$ (right) by the down and up projections of Definition~\ref{def:downUpProjections}. For space reasons, $\projUp(S\ex)$ is only represented partially: the remaining strings are obtained by adding independently the two dotted arrows to all strings containing their left endpoint.}
	\label{fig:exmProjections}
\end{figure}
\end{example}

@@

\begin{example}
The map~$\eta$ is illustrated on \fref{fig:exmSurjection}\,(left) for the gentle bound quiver~$\bar Q\ex$ of \fref{fig:exmBlossomingQuiver}\,(left).

\begin{figure}[t]
	\capstart
	\centerline{
	\begin{overpic}[scale=.45]{exmSurjection}
			\put(28,8){$\longrightarrow$}
			\put(29,10){$\eta$}
			\put(69,8){$\longrightarrow$}
			\put(70,10){$\zeta$}
			\put(13,-3){$S\ex$}
			\put(46,-3){$\eta(S\ex)$}
			\put(77,-3){$\zeta(\eta(S\ex)) = \projDown(S\ex)$}
	\end{overpic}
	}
	\vspace{.3cm}
	\caption{The maps~$\eta$ of Definition~\ref{def:eta} from biclosed sets to non-kissing facets (left) and $\zeta$ of Definition~\ref{def:zeta} from non-kissing facets to biclosed sets (right).}
	\label{fig:exmSurjection}
\end{figure}
\end{example}

@@

\begin{example}
The map~$\zeta$ is illustrated on \fref{fig:exmSurjection}\,(right)  for the gentle bound quiver~$\bar Q\ex$ of \fref{fig:exmBlossomingQuiver}\,(left).
\end{example}

@@

\begin{example}
The $\b{g}$-vector of the plain blue walk on \fref{fig:exmFacet}\,(left) is~$(0,-1,0,0,1,0)$ (see \fref{fig:exmBlossomingQuiver} for the labeling order of the vertices of the quiver~$Q\ex$).
See \fref{fig:gcvectors} for more examples of $\b{g}$-vectors.
\end{example}

@@

\begin{example}
In the facet~$F\ex$ of \fref{fig:exmFacet}\,(right), the $\b{c}$-vector of the blue walk is~$(0,-1,0,0,0,0)$ while the $\b{c}$-vector of the yellow path is~$(0,1,0,1,1,0)$ (see \fref{fig:exmBlossomingQuiver} for the labeling order of the vertices of the quiver~$Q\ex$ and \fref{fig:gcvectors}\,(left) to see the distinguished arrows in the facet~$F\ex$).
See \fref{fig:gcvectors} for more examples of $\b{c}$-vectors.

\begin{figure}[t]
	\capstart
	\centerline{$\raisebox{-1.5cm}{\begin{overpic}[scale=.7]{exmVectors}\put(60,4){$F\ex$}\end{overpic}}$ \qquad \input{gcmatrices}}
	\caption{The $\b{g}$- and $\b{c}$-matrices of the facet~$F\ex$. Their columns correspond to the $\b{g}$- and $\b{c}$-vectors of the different walks of~$F\ex$. See \fref{fig:exmBlossomingQuiver} for the labeling order of the vertices of the quiver~$Q\ex$. Note that~$\gvectors{F\ex} \cdot \cvectors{F\ex}^T = \one$.}
	\label{fig:gcvectors}
\end{figure}
\end{example}

>>>>

\begin{example}
A gentle bound quiver~$\bar Q$ and its blossoming gentle bound quiver~$\bar Q\blossom$ are represented in \fref{fig:exmBlossomingQuiver}.
\vspace*{-.4cm}

\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=.7]{exmBlossomingQuiver}}
	\caption{A gentle bound quiver~$\bar Q$~(left) and its blossoming gentle bound quiver~$\bar Q\blossom$~(right). Blossom vertices are white and blossom edges are thin.}
	\label{fig:exmBlossomingQuiver}
\end{figure}
\end{example}

@@

\begin{definition}
A \defn{walk} of~$\bar Q$ is a maximal string in~$\bar Q\blossom$ (thus joining two blossom vertices of~$\bar Q\blossom$).
We denote by~$\walks(\bar Q)$ the set of all walks on~$\bar Q$.
Note that~$\walks(\bar Q)$ is finite if and only if~$\bar Q$ has a relation in any (not necessarily oriented) cycle.
As for strings, we often implicitly identify the two inverse walks~$\omega$ and~$\omega^{-1}$, and we let~$\walks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \walks(\bar Q)}$ denote the set of undirected~walks.
\end{definition}

\begin{example}
\fref{fig:exmFacet} shows many examples of walks on the gentle quiver of \fref{fig:exmBlossomingQuiver}.
\end{example}

@@

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=1.4]{exmBijectionAssociahedron}}
	\caption{An oriented path~$\exmAn$ is simultaneously a triangulation and a grid bound quiver (left). A facet of the reduced non-kissing complex~$\RNKC[\exmAn]$ can be seen equivalently as a triangulation or as a collection of non-kissing south-east paths (right).}
	\label{fig:exmBijectionAssociahedron}
\end{figure}

@@

\begin{example}
\fref{fig:exmFacet}~(left) provides examples of kissing and non-kissing walks.
%
\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.7]{exmFacet}}
	\caption{(Left) Three walks on the bound quiver~$\bar Q$ of \fref{fig:exmBlossomingQuiver}: the dotted red and orange walks are non-kissing, but both kiss the plain blue walk. (Right) A maximal collection~$F$ of pairwise non-kissing walks on~$\bar Q$: the thin light blue walks are straight, the others~are~bending.}
	\label{fig:exmFacet}
\end{figure}
\end{example}

@@

\begin{example}
\fref{fig:exmFacet}\,(right) shows a facet~$F$ of the non-kissing complex~$\NKC[\bar Q]$ for the bound quiver~$\bar Q$ of \fref{fig:exmBlossomingQuiver}.
The reduced non-kissing complexes of all connected gentle bound quivers with~$2$ vertices are illustrated on \fref{fig:all2}.
The reduced non-kissing complexes of two gentle bound quivers with~$3$ vertices are illustrated on \fref{fig:exmNKC}\,(left).
\end{example}

@@

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.7]{exmFlip}}
	\caption{The flip of the orange walk~$\omega$ in the facet~$F$ of \fref{fig:exmFacet}. The other two walks~$\mu, \nu$ of~$F$ involved in the flip are the yellow and green walks. The distinguished arrows on each walk of~$F$ are marked with triple arrows.}
	\label{fig:exmFlip}
\end{figure}

@@

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.45]{exmBiclosed}}
	\caption{Four sets of strings on the gentle bound quiver~$\bar Q$ of \fref{fig:exmBlossomingQuiver}\,(left). The first is neither closed not coclosed, the second is closed but not coclosed, the third is coclosed but not closed, and the fourth is biclosed.}
	\label{fig:exmBiclosed}
\end{figure}
\end{example}

@@

\begin{figure}[t]
	\capstart
	\centerline{
	\begin{overpic}[scale=.45]{exmProjections}
			\put(30,6){$\longleftarrow$}
			\put(31,8){$\projDown$}
			\put(68,6){$\longrightarrow$}
			\put(69,8){$\projUp$}
			\put(12,-3){$\projDown(S)$}
			\put(50,-3){$S$}
			\put(85,-3){$\projUp(S)$}
	\end{overpic}
	}
	\vspace{.3cm}
	\caption{A biclosed set of strings~$S \in \Bicl{\bar Q\}$ (middle), where~$\bar Q$ is the bound quiver of~\fref{fig:exmBlossomingQuiver}, and its images~$\projDown(S)$ (left) and~$\projUp(S)$ (right) by the down and up projections of Definition~\ref{def:downUpProjections}. For space reasons, $\projUp(S)$ is only represented partially: the remaining strings are obtained by adding independently the two dotted arrows to all strings containing their left endpoint.}
	\label{fig:exmProjections}
\end{figure}
\end{example}

@@

\begin{example}
The map~$\eta$ is illustrated on \fref{fig:exmSurjection}\,(left) for the gentle bound quiver~$\bar Q$ of \fref{fig:exmBlossomingQuiver}\,(left).

\begin{figure}[t]
	\capstart
	\centerline{
	\begin{overpic}[scale=.45]{exmSurjection}
			\put(28,8){$\longrightarrow$}
			\put(29,10){$\eta$}
			\put(69,8){$\longrightarrow$}
			\put(70,10){$\zeta$}
			\put(13,-3){$S$}
			\put(46,-3){$\eta(S)$}
			\put(77,-3){$\zeta(\eta(S)) = \projDown(S)$}
	\end{overpic}
	}
	\vspace{.3cm}
	\caption{The maps~$\eta$ of Definition~\ref{def:eta} from biclosed sets to non-kissing facets (left) and $\zeta$ of Definition~\ref{def:zeta} from non-kissing facets to biclosed sets (right).}
	\label{fig:exmSurjection}
\end{figure}
\end{example}

@@

\begin{example}
The map~$\zeta$ is illustrated on \fref{fig:exmSurjection}\,(right)  for the gentle bound quiver~$\bar Q$ of \fref{fig:exmBlossomingQuiver}\,(left).
\end{example}

@@

\begin{example}
The $\b{g}$-vector of the plain blue walk on \fref{fig:exmFacet}\,(left) is~$(0,-1,0,0,1,0)$ (see \fref{fig:exmBlossomingQuiver} for the labeling order of the vertices of the quiver~$Q$).
See \fref{fig:gcvectors} for more examples of $\b{g}$-vectors.
\end{example}

@@

\begin{example}
In the facet~$F$ of \fref{fig:exmFacet}\,(right), the $\b{c}$-vector of the blue walk is~$(0,-1,0,0,0,0)$ while the $\b{c}$-vector of the yellow path is~$(0,1,0,1,1,0)$ (see \fref{fig:exmBlossomingQuiver} for the labeling order of the vertices of the quiver~$Q$ and \fref{fig:gcvectors}\,(left) to see the distinguished arrows in the facet~$F$).
See \fref{fig:gcvectors} for more examples of $\b{c}$-vectors.

\begin{figure}[t]
	\capstart
	\centerline{$\raisebox{-1.5cm}{\begin{overpic}[scale=.7]{exmVectors}\put(60,4){$F$}\end{overpic}}$ \qquad \input{gcmatrices}}
	\caption{The $\b{g}$- and $\b{c}$-matrices of the facet~$F$ of \fref{fig:exmFacet}. Their columns correspond to the $\b{g}$- and $\b{c}$-vectors of the different walks of~$F$. See \fref{fig:exmBlossomingQuiver} for the labeling order of the vertices of the quiver~$Q$. Note that~$\gvectors{F} \cdot \cvectors{F}^T = \one$.}
	\label{fig:gcvectors}
\end{figure}
\end{example}
